---
title: "Created Augmented pred/ipred plots with `augPred()`"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a simple process to create individual predictions augmented
with more observations than was modeled.  This allows smoother plots
and a better examination of the observed concentrations for an
individual and population.

# Step 1: Convert the `Monolix` model to `rxode2`:

```{r setup}

library(monolix2rx)

# First we need the location of the nonmem control stream Since we are
# running an example, we will use one of the built-in examples in
# `monolix2rx`
pkgTheo <- system.file("theo/theophylline_project.mlxtran", package="monolix2rx")
# You can use a control stream or other file. With the development
# version of `babelmixr2`, you can simply point to the listing file

mod <- monolix2rx(pkgTheo)

```


# Step 2: convert the `rxode2` model to `nlmixr2`

In this step, you convert the model to `nlmixr2` by `as.nlmixr2(mod)`;
You may need to do a [little manual work to get the residual
specification to match between nlmixr2 and NONMEM](convert-nlmixr2.html).

Once the residual specification is compatible with a nlmixr2 object, you can convert the model, `mod`, to a nlmixr2 fit object:

```{r toNlmixr2}
library(babelmixr2) # provides as.nlmixr2
fit <- as.nlmixr2(mod)

fit
```

# Step 3: Create and plot an augmented prediction

```{r augPred}
ap <- augPred(fit)

head(ap)

# This augpred looks odd:
plot(ap)
```
