---
title: "Easily Create a VPC using monolix2rx"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
This shows an easy work-flow to create a VPC using a Monolix model:

# Step 1: Convert the `Monolix` model to `rxode2`:

```{r setup}
library(babelmixr2)
library(monolix2rx)

# First we need the location of the monolix mlxtran file. Since we are
# running an example, we will use one of the built-in examples in
# `monolix2rx`
pkgTheo <- system.file("theo/theophylline_project.mlxtran", package="monolix2rx")
# You can use a control stream or other file. With the development
# version of `babelmixr2`, you can simply point to the listing file

mod <- monolix2rx(pkgTheo)

```


# Step 2: convert the `rxode2` model to `nlmixr2`

You can convert the model, `mod`, to a nlmixr2 fit object:

```{r toNlmixr2}
fit <- as.nlmixr2(mod)

fit
```

# Step 3: Perform the VPC

From here we simply use `vpcPlot()` in conjunction with the `vpc`
package to get the regular and prediction-corrected VPCs and arrange
them on a single plot:

```{r vpc}

library(ggplot2)
p1 <- vpcPlot(fit, show=list(obs_dv=TRUE))

p1 <- p1 + ylab("Concentrations") +
  rxode2::rxTheme() +
  xlab("Time (hr)") +
  xgxr::xgx_scale_x_time_units("hour", "hour")

p1a <- p1 + xgxr::xgx_scale_y_log10()

## A prediction-corrected VPC
p2 <- vpcPlot(fit, pred_corr = TRUE, show=list(obs_dv=TRUE))
p2 <- p2 + ylab("Prediction-Corrected Concentrations") +
  rxode2::rxTheme() +
  xlab("Time (hr)") +
  xgxr::xgx_scale_x_time_units("hour", "hour")

p2a <- p2 + xgxr::xgx_scale_y_log10()


library(patchwork)
(p1 * p1a) / (p2 * p2a)
```
