---
title: "Qualify rxode2 model against Monolix"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Qualify rxode2 model against Monolix}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(rxode2)
setRxThreads(1L)
library(data.table)
setDTthreads(1L)
```


```{r setup}

library(monolix2rx)
# You use the path to the monolix mlxtran file

# In this case we will us the theophylline project included in monolix2rx
pkgTheo <- system.file("theo/theophylline_project.mlxtran", package="monolix2rx")

# Note you have to setup monolix2rx to use the model library or save the model as a separate file
mod <- monolix2rx(pkgTheo)

print(mod)

```

### Comparing differences between `Monolix` and `rxode2`

You may wish to see where the differences in predictions are between
Monolix and rxode2.

The `rxode2` generated outputs are compared with the `Monolix`
generated outputs for the following items:

- **Population Predictions:** this shows if the model translation is
  adequate to simulate general trends; This will validate structural
  model's population parameters coupled with the model structure.

- **Individual Predictions:** this shows if the model translation is
  able to replicate the same values over all the subjects within the
  modeling data-set.  This validates the model can reproduce the
  between subject variability observed in the study.

- **Individual Weighted Residuals:** this is one step further than the
  individual parameter validation, it couples the individual
  predictions, the observations and the residual specification to
  generate the individual weighted residuals. This is included to be
  consistent with the `nonmem2rx` residuals.  However, since this is
  not needed to manually adjust the residual errors, this simply looks
  at if the errors were converted correctly.

**Note:** the only part that is not validated with these three metrics
is the between subject covariance matrix, `omega`. We assume this is
correct as long as it is read in correctly.

## Comparing numerically

If you want numerical differences, you can also get these from the
modified returned `ui` object.  For the rtol, atol as follows you have:

```{r tol}
mod$iwresAtol
mod$iwresRtol
mod$ipredAtol
mod$ipredRtol
mod$predAtol
mod$predAtol
```

You can see they do not exactly match but are very close (I would say
they validate). However you can explore these difference further if you wish
by looking at the `ipredCompare` and `predCompare` datasets:

```{r compare}
head(mod$iwresCompare)

head(mod$ipredCompare)

head(mod$predCompare)
```

In these cases you can see that Monolix seems to round the values to 5
digits, while `rxode2` keeps everything since it is solved in R
directly.

Note this is the **observation data only** that is compared.  Dosing
predictions are excluded from these comparisons.

You can also explore the Monolix translated input dataset that was
used to make the validation predictions (dosing and observations) by
the `$monolixData` item:

```{r monolixData}
head(mod$monolixData) # with nlme loaded you can also use getData(mod)
```

## Comparing visually

The easiest way to visually compare the differences is by the plot method:

```{r plot}

plot(mod) # for general plot

# you can also see individual comparisons
plot(mod, log="y", ncol=2, nrow=2,
     xlab="Time (hr)", ylab="Concentrations",
     page=1)

# If you want all pages you could use:
#
plot(mod, log="y", ncol=2, nrow=2,
     xlab="Time (hr)", ylab="Concentrations",
     page=TRUE)
```


## Notes on validation

The validation of the model uses the best data available for Monolix
estimates.  This is:

- `theta` or population parameters
- `eta` or individual parameters

The `omega` and `sigma` matrices are captured. When the nlmixr2 model
is fully qualified, the `IWRES` validation ensures the residual errors
are specified correctly. Otherwise `omega` and `sigma` values do not contribute to
the validation.  Also the overall covariance is captured, but not used
in the validation.
