---
title: "Simulate using Parameter Uncertainty"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simulate using Parameter Uncertainty}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(rxode2)
setRxThreads(1L)
library(data.table)
setDTthreads(1L)
```

This page shows a simple work-flow for directly simulating a different
dosing paradigm than what was modeled taking into account the modeled
uncertainty. This workflow is very similar to simply [simulating
without uncertainty](simulate-new-dosing.html) in the parameters
themselves.

## Step 1: Import the model

```{r setup}

library(monolix2rx)
library(rxode2)
# its best practice to set the seed for the simulations
set.seed(42)
rxSetSeed(42)


# You use the path to the monolix mlxtran file

# In this case we will us the theophylline project included in monolix2rx
pkgTheo <- system.file("theo/theophylline_project.mlxtran", package="monolix2rx")

# Note you have to setup monolix2rx to use the model library or save
# the model as a separate file
mod <- monolix2rx(pkgTheo)

print(mod)
```
## Step 2: Look at a different dosing paradigm

Lets say that in this case instead of a single dose, we want to see
what the concentration profile is with a single day of BID dosing.  In
this case is done by creating a [quick event
table](https://nlmixr2.github.io/rxode2/articles/rxode2-event-table.html).

```{r eventTable}
ev <- et(amt=4, ii=12, until=24) %>%
  et(c(1:6, seq(8, 24, by=2))) %>%
  et(id=1:100)
```



## Step 3: Solve using the uncertainty in the NONMEM model

To use the uncertainty in the model, it is a simple matter of telling
how many times `rxode2()` should sample with `nStud=X`.  In this case
we will use `100`.

```{r rxSolve}
s <- rxSolve(mod, ev, nStud=100)

s
```


## Step 4: Summarize and plot

Since there is a bunch of data, a confidence band of the simulation with uncertainty would be helpful.

One way to do that is to select the interesting components, create a confidence interval and then plot the confidence bands:



```{r confint}
sci <- confint(s, parm=c("CONC", "sim"))

sci

p1 <- plot(sci)

p2 <- plot(sci, log="y")

library(patchwork)

p1/p2

```
