---
title: "Simulate New dosing from Monolix model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simulate New dosing from Monolix model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(rxode2)
setRxThreads(1L)
library(data.table)
setDTthreads(1L)
```

This page shows a simple work-flow for directly simulating a different
dosing paradigm than what was modeled.


## Step 1: Import the model

```{r setup}
library(monolix2rx)
library(rxode2)

library(monolix2rx)
# You use the path to the monolix mlxtran file

library(monolix2rx)
# You use the path to the monolix mlxtran file

# In this case we will us the theophylline project included in monolix2rx
pkgTheo <- system.file("theo/theophylline_project.mlxtran", package="monolix2rx")

# Note you have to setup monolix2rx to use the model library or save
# the model as a separate file
mod <- monolix2rx(pkgTheo)

print(mod)

```

## Step 2: Look at a different dosing paradigm

Lets say that in this case instead of a single dose, we want to see
what the concentration profile is with a single day of BID dosing.
In this case is done by creating a [quick event table](https://nlmixr2.github.io/rxode2/articles/rxode2-event-table.html):

```{r eventTable}
ev <- et(amt=4, ii=12, until=24) %>%
  et(list(c(0, 2), # add observations in windows
          c(4, 6),
          c(8, 12),
          c(14, 18),
          c(20, 26),
          c(28, 32),
          c(32, 36),
          c(36, 44))) %>%
  et(id=1:10)
```

## Step 3: solve using `rxode2`

In this step, we solve the model with the new event table for the 10
subjects:

```{r solve}
s <- rxSolve(mod, ev)
```

Note that since this is a `nonmem2rx` model, the default solving will
match the tolerances and methods specified in your `NONMEM` model.

## Step 4: exploring the simulation (by plotting)

This solved object acts the same as any other `rxode2` solved object,
so you can use the `plot()` function to see the individual profiles
you simulated:

```{r plot}
library(ggplot2)
plot(s, ipredSim) +
  ylab("Concentrations")
```
